\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=1in,top=1.3in,right=1in,bottom=1.3in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{etaremune}
\usepackage[inline]{enumitem} 
\usepackage{graphicx}
\usepackage{tabularx}
\pagestyle{plain}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Songyuan Zhang}
\lhead{Curriculum Vitae}
\rfoot{Page \thepage}

\hypersetup{
% 	bookmarks=true,         % show bookmarks bar?
	unicode=false,          % non-Latin characters in Acrobat’s bookmarks
	pdftoolbar=true,        % show Acrobat’s toolbar?
	pdfmenubar=true,        % show Acrobat’s menu?
	pdffitwindow=false,     % window fit to page when opened
	pdfstartview={FitH},    % fits the width of the page to the window
	pdftitle={Resume of Songyuan Zhang},    % title
	pdfauthor={Songyuan Zhang},     % author
	pdfsubject={Resume},   % subject of the document
	pdfcreator={Songyuan Zhang},   % creator of the document
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,          % color of internal links (change box color with linkbordercolor)
	citecolor=green,        % color of links to bibliography
	filecolor=magenta,      % color of file links
	urlcolor=blue           % color of external links
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\paperItem}[4]{#1.~``#2."~\textit{#3},~#4.}%author title venue year
\newcommand{\talktitle}[1]{{``#1",}} %talk title
\newcommand{\talkplace}[3]{{\textit{#1},~#2,~#3.}} % conference, place, time
\newcommand{\confItem}[3]{#1~#2~(\textit{#3})} %abrrev, full name, year
\newcommand{\patentItem}[3]{``#1",~#2,~#3.} % title, number, date

\newcommand{\me}{\underline{Songyuan Zhang}}
\newcommand{\meshort}{\textbf{S. Zhang}}
\newcommand{\person}[2]{#1}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

    
\makeatletter
% This command ignores the optional argument for itemize and enumerate lists
\newcommand{\inlineitem}[1][]{%
	\ifnum\enit@type=\tw@
	{\descriptionlabel{#1}}
	\hspace{\labelsep}%
	\else
	\ifnum\enit@type=\z@
	\refstepcounter{\@listctr}\fi
	\quad\@itemlabel\hspace{\labelsep}%
	\fi}
\makeatother

\name{Songyuan Zhang}
\address{{\bf LAB:} REALM Lab, MIT Building 31, 70 Vassar St, Cambridge, MA 02139, U.S.}
\address{{\bf EMAIL:} \href{mailto:szhang21@mit.edu}{\nolinkurl{szhang21@mit.edu}}}
\address{{\bf HOMEPAGE:} \href{http://syzhang092218-source.github.io}{http://syzhang092218-source.github.io}}

\begin{document}
	\begin{rSection}{RESEARCH INTERESTS}
		Safe Autonomous Systems, Machine Learning, Reinforcement Learning, Robotics, Control Theory
	\end{rSection}

	\begin{rSection}{Education} 		
		% \small
		\begin{rSubsection2}{Massachusetts Institute of Technology}{Aug. 2021 - Now}{Graduate Student at Department of Aeronautics and Astronautics}{Advisor: Prof. Chuchu Fan}
		\end{rSubsection2} 
	
		\begin{rSubsection2}{Tsinghua University}{Sep. 2017 - Jul. 2021}{B.E. in Tsien Excellence in Engineering Program (honored degree)}{\\\rightline{Advisor: Prof. Yanan Sui, Prof. Hao Wu, Prof. Gangtie Zheng}} 
		\end{rSubsection2}
		\vspace{-10pt}
        
        \begin{rSubsection2}{Stanford University}{Jun. 2020 - July. 2021}{Remote Visiting Scholar in Computer Science}{Advisor: Prof. Dorsa Sadigh}
		\end{rSubsection2}

		\begin{rSubsection2}{University of California, Berkeley}{July. 2019 - Sept. 2019}{Visiting Scholar in Mechanical Engineering}{Advisor: Prof. Masayoshi Tomizuka}
		\end{rSubsection2}
	\end{rSection}

	\begin{rSection}{Publications}
		\item[] \textbf{\underline{JOURNAL}}
		\vspace{5pt}
		{
			\item {\bf [SG'23]}
			\paperItem{\person{Lizhi Wang}{L. Wang}, \person{\me}{\meshort}, \person{Yifan Zhou}{Y. Zhou}, \person{Chuchu Fan}{C. Fan}, \person{Peng Zhang}{P. Zhang}, and \person{Yacov A. Shamash}{YA. Shamash}}{Physics-Informed, Safety and Stability Certified Neural Control for Uncertain Networked Microgrids}{IEEE Transactions on Smart Grid}{2023}{\href{https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=10233047}{[PDF]}}
		}
		\vspace{5pt}
		\item[] \textbf{\underline{CONFERENCE}}
		\vspace{5pt}
		{
			\item {\bf [CoRL'23]}
			\paperItem{\person{\me}{\meshort}, \person{Kunal Garg}{K. Garg}, and \person{Chuchu Fan}{C. Fan}}{Neural Graph Control Barrier Functions Guided Distributed Collision-avoidance Multi-agent Control}{7th Conference on Robot Learning (CoRL 2023)}{2023}{\href{https://mit-realm.github.io/gcbf-website/}{[Website]}}
			\item {\bf [L4DC'23 (ORAL)]}
			\paperItem{\person{\me}{\meshort}, \person{Yumeng Xiu}{Y. Xiu}, \person{Guannan Qu}{G. Qu}, and \person{Chuchu Fan}{C. Fan}}{Compositional Neural Certificates for Networked Dynamical Systems}{5th Annual Learning for Dynamics \& Control Conference (L4DC)}{2023}{\href{https://mit-realm.github.io/neuriss-website/}{[Website]}}
			\item {\bf [NeurIPS'21]}
			\paperItem{\person{\me*}{\meshort}, \person{Zhangjie Cao*}{Z. Cao}, \person{Dorsa Sadigh}{D. Sadigh}, and \person{Yanan Sui}{Y. Sui}}{Confidence-Aware Imitation Learning from Demonstrations with Varying Optimality}{Conference on Neural Information Processing Systems}{2021}{\href{https://sites.google.com/view/cail/}{[Website]}}
		}
	\end{rSection}

	\begin{rSection}{Honors and Awards} {} \itemsep -2pt {}  
		% \small
		\item Outstanding Graduate of Tsinghua University \hfill{2021}
		\item Outstanding Graduate of Beijing \hfill{2021}
		\item Outstanding Graduate of Scientific Research at TEEP \hfill{2021}
		\item Outstanding Graduate of Creativity at TEEP \hfill{2021}
		\item Honor Degree of Tsien Class, Tsinghua University \hfill{2021}
		\item Tsinghua Scholarship for Technological Innovation \hfill{2020}
		\item National Scholarship, China \hfill{2019}
		\item First Prize in Excellent Student Research Training Contest of Tsinghua University \hfill{2019}
		\item First Prize in "Challenge Cup" Science and Technology Competition of Tsinghua University \hfill{2019}
	\end{rSection}

	\begin{rSection}{ACADEMIC SERVICES}
		\item \textbf{Teaching Assistant} at Tsinghua University: X-idea (2021 Spring)
	\end{rSection}

	\begin{rSection}{LEADERSHIP \& MEMBERSHIP}
		\item Chairman of 13th \textsl{Spark} Innovative Talents Training Program at Tsinghua University
		\item Vice-monitor of Tsien Class 2017
		\item Member of the Second Team of Middle and Long Distance Running at Tsinghua University
	\end{rSection}

	\begin{rSection}{HOBBIES}
		\item Photography, Badminton, Running, Skiing, Piano, Drum kit, Taekwondo, Poker Magic
	\end{rSection}
	
\end{document}
